A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-03 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
modified agent table to be for just one agent
deciding how to configure tabel
moved agent table to end of paper

ADD table for Agent types
\begin{table}[htbp]
    \caption{Agent Types}
    \begin{center}
    \begin{tabular}{|c|c|c|c|}
    \hline
    \textbf{Parameters}&\multicolumn{3}{|c|}{\textbf{Agents}} \\
    \cline{2-4} 
    \textbf{ } & \textbf{\textit{Node}}& \textbf{\textit{Group}}& \textbf{\textit{Signature}} \\
    \hline
    Unique ID & X & X & X \\
    \hline
    \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{table}
    \end{center}
    \end{table}

@@

>>>>

ADD table for Agent types

@@

\newpage
\begin{table}[htbp]
    \caption{Node Agent}
    \begin{center}
    \begin{tabular}{|c|c|}
    \cline{1-2} 
    \textbf{Key Attributes}&{\textbf{Node Agent}} \\
    \cline{1-2} 
    \hline
    Connection Delay & Delay between when a node is created and when it can join the network \\
    Ticket List & List of random numbers used to pick the node for participation in a group\\
    Connection Failure Percent & Likelihood of disconnecting from the network\\
    Death Percent & Likelihood of going offline and never re-connecting\\
    Malicousness & determines if a node is considered malicous based on if the operator is malicious\\
    Operator  & the entity that runs this node\\
    \hline
    \textbf{ }&\textbf{Group Agent} \\
    \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{table}
    \end{center}
    \end{table}
